### 2024-04-04 doc/15yrsChange.Rmd
figure 1 changes and citation updates

The study was conducted in the 25.6-hectare Forest Dynamics plot at the Smithsonian’s National Zoo and Conservation Biology Institute (SCBI) in Front Royal, Virginia (38$^\circ$ 53' 36.6''N, 78$^\circ$  08’ 43.4''W). The forest dynamics plot, which is located in the central Appalachian Mountains adjacent to Shenandoah National Park, is composed of mature secondary eastern deciduous forest. As part of the Appalachian Oak forest region, the canopy is dominated by tulip poplar (*Liriodendron tulipifera*), oak (*Quercus* spp.), and hickory (*Carya* spp.) and the understory is primarily composed of spicebush (*Lindera benzoin*), paw-paw (*Asimina triloba*), American hornbeam (*Carpinus caroliniana*), and witch hazel (*Hamamelis virginiana*). The land-use history of the site is varied, including periods of agricultural development and intensive logging, with dendrological data estimating canopy tree establishment around 1900 [SI archives, @bourg_initial_2013. The plot, which includes a four-hectare deer exclosure that has decreased the presence of deer since 1990, is divided into 640 quadrats, each measuring 20 x 20 meters. It is one of 78 sites in the Forest Global Earth Observatory (ForestGEO), a global network of forest dynamic plots that facilitates comparative forest ecology studies around the world [@anderson-teixeira_ctfsforestgeo_2015; @davies_forestgeo_2021].

>>>>

The study was conducted in the 25.6-hectare Forest Dynamics plot at the Smithsonian’s National Zoo and Conservation Biology Institute (SCBI) in Front Royal, Virginia (38$^\circ$ 53' 36.6''N, 78$^\circ$  08’ 43.4''W). The forest dynamics plot, which is located in the central Appalachian Mountains adjacent to Shenandoah National Park, is composed of mature secondary eastern deciduous forest. As part of the Appalachian Oak forest region, the canopy is dominated by tulip poplar (*Liriodendron tulipifera*), oak (*Quercus* spp.), and hickory (*Carya* spp.) and the understory is primarily composed of spicebush (*Lindera benzoin*), paw-paw (*Asimina triloba*), American hornbeam (*Carpinus caroliniana*), and witch hazel (*Hamamelis virginiana*). The land-use history of the site is varied, including periods of agricultural development and intensive logging, with dendrological data estimating canopy tree establishment around 1900 [SI archives, @bourg_initial_2013, @mcgarvey_effects_2013a] The plot, which includes a four-hectare deer exclosure that has decreased the presence of deer since 1990, is divided into 640 quadrats, each measuring 20 x 20 meters. It is one of 78 sites in the Forest Global Earth Observatory (ForestGEO), a global network of forest dynamic plots that facilitates comparative forest ecology studies around the world [@anderson-teixeira_ctfsforestgeo_2015; @davies_forestgeo_2021].
